---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE,eval = FALSE)
devtools::load_all(".")
```

# eqdata <img src="inst/figures/eq_hex.svg" width="250" height="250" align="right" />

`eqdata` provides financial data from [Financial Modeling Prep](https://financialmodelingprep.com/developer/docs/ "FMP Dev Site")

# install

```{r,eval=FALSE}
devtools::install_github("zac-garland/eqdata")
library(eqdata)
```


# pricing data 
***

* `q_intraday : function (ticker, freq = c("1min", "5min", "15min", "30min", "1hour"))`
* `q_price : function (ticker)`  
* `q_divs : function (ticker)`
* `q_splits : function (ticker)`

# financial statements 
***

* `q_income_statement(ticker, freq = c("quarterly", "annual"))`
* `q_balance_sheet(ticker, freq = c("quarterly", "annual"))`
* `q_cash_flow_statement(ticker, freq = c("quarterly", "annual"))`


# company meta 
***

* `q_company_profile(ticker)`
* `q_company_quote(ticker)`
* `q_company_rating(ticker)`


# ratios & calcs 
***

* `q_discount_cash_flow(ticker, freq = c("quarterly", "annual"))`
* `q_enterprise_value(ticker, freq = c("quarterly", "annual"))`
* `q_growth_ratios(ticker, freq = c("quarterly", "annual"))`
* `q_key_ratios(ticker, freq = c("quarterly", "annual"))`
* `q_financial_ratios(ticker)`


# general 
***

* `q_all_stock_price()`
* `q_stock_list()`
* `q_ticker_search("AA", limit = 10)`

